Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-03-10 manuscript/appendix.Rmd
rearranged SI fig. order
#65

  knitr::include_graphics("tables_figures/climate_regressions.png")
```
\elandscape

```{r echo=FALSE, fig.cap = "Figure S3: Individual plots of FACF in relation to mean annual climate, part 1.", out.height='95%', fig.pos='H'}

@@

```{r echo=FALSE, fig.cap = "Figure S4: Individual plots of FACF in relation to mean annual climate, part 2.", out.height='95%', fig.pos='H'}

@@

```{r echo=FALSE, fig.cap = "Figure S5: Individual plots of FACF in relation to mean climate seasonality, part 1.", out.height ='95%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S6: Individual plots of FACF in relation to mean climate seasonality, part 2.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S7: Growing season length-standardized FACF in relation to mean growing season climate, part 1.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S8: Growing season length-standardized FACF in relation to mean growing season climate, part 2.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S9: Ratios among FACF as a function of latitude and climate variables", out.width ='100%', fig.pos='H'}

>>>>

  knitr::include_graphics("tables_figures/climate_regressions.png")
```
\elandscape
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S3: Ratios among FACF as a function of latitude and climate variables", out.width ='100%', fig.pos='H'}

\blandscape
```{r echo=FALSE, fig.cap = "Figure S4: Individual plots of FACF in relation to mean annual climate, part 1.", out.height='95%', fig.pos='H'}

@@

```{r echo=FALSE, fig.cap = "Figure S5: Individual plots of FACF in relation to mean annual climate, part 2.", out.height='95%', fig.pos='H'}

@@

```{r echo=FALSE, fig.cap = "Figure S6: Individual plots of FACF in relation to mean climate seasonality, part 1.", out.height ='95%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S7: Individual plots of FACF in relation to mean climate seasonality, part 2.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S8: Growing season length-standardized FACF in relation to mean growing season climate, part 1.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S9: Growing season length-standardized FACF in relation to mean growing season climate, part 2.", out.width ='100%', fig.pos='H'}

@@
